% Copyright (C) 2019-2021 by Cheng XU <copyright@xuc.me>
% All Rights Reserved.

\documentclass{mycv}

\name[Chen ZUO]{Chen ZUO \small{MEng}}
\address{Miyamoto Lab, Tokyo Institute of Technology \\ 4259 Nagatsuta, Yokohama, Kanagawa}
\email{zuo.c.aa@m.titech.ac.jp}
%\homepage{https://xuc.me}
\github{realzuoc}
\linkedin{chen-zuo}

\begin{document}

\maketitle%

\begin{summary}
Specializing in the development of Optical Wireless Power Transmission (OWPT) applications and Laser safety technology, I bring a robust background in the design and implementation of VCSEL-based systems and the advanced safety solutions towards the operation of Lasers. My academic foundation encompasses optical design, semiconductor physics, and photovoltaic, complemented by practical skills in computer vision, system control, and automation. I excel at integrating these disciplines to innovate and enhance system efficiencies in OWPT projects.
\end{summary}

\section{Professional \\ Experience}

\subsection{\href{http://vcsel-www.pi.titech.ac.jp/index-j.html}{Miyamoto Lab, Tokyo Institute of Technology}}[Kanagawa, Japan]
\begin{positions}
  \entry{PhD Course Student}{Oct 2021~--~Present}
\end{positions}
\begin{itemize}
	\item Advisor: \href{https://www.first.iir.titech.ac.jp/member/core3.html#miyamoto}{Associate Prof.~Tomoyuki Miyamoto}
	\item Theme: Advanced Optical Wireless Power Transmission Safety System towards Error-free Safety
\end{itemize}

%\subsection{NTT Space Environment and Energy Laboratories, NTT R\&D}[Tokyo, Japan]
%\begin{positions}
%	\entry{Internship}{Aug 2023~--~Sept 2023}
%\end{positions}
%\begin{itemize}
%	\item Project: Study on cell connection optimization of photoelectric conversion device in laser energy transmission.
%\end{itemize}

\subsection{\href{https://www.iir.titech.ac.jp/en/}{FIRST, IIR, Tokyo Institute of Technology}}[Kanagawa, Japan]
\begin{positions}
  \entry{Research Assistant}{Oct 2022~--~Present}
\end{positions}
\begin{itemize}
	\item Project: Development of the IoT application and the control system for indoor Optical Wireless Power Transmission System. 
\end{itemize}



\section{Research \\ Outcomes}

\begin{enumerate}
  \item Advanced OWPT Safety System towards Error-free Safety. \printdate{ongoing}
  \item Fundamental Investigation of Camera-based Safety System of OWPT. \printdate{July 2023}
  \item OWPT using VCSEL and GaAs Solarcell. \printdate{Jan 2021}
  \item A Novel GaN Power Converter. \printdate{Aug 2020}
  \item Arduino-based smart home system development. \printdate{Apr 2020}
  \item Photoelectric Detection Based Auto-Tracing PID Smart Car. \printdate{Oct 2019}
\end{enumerate}

\section{Education}

\subsection{Tokyo Institute of Technology}[Tokyo, Japan]
\vspace{-\parskip}%
\begin{itemize}[label={}]	
  \item MEng.\ in Electrical and Electronic Engineering \printdate{Nov 2021~--~July 2023}
  \item Dissertation: {Fundamental Investigation of Camera-based Safety System of Optical Wireless Power Transmission} (Top 10\% With Outstanding Award)%\href{https://scholars.hkbu.edu.hk/en/studentTheses/authenticated-query-processing-in-the-cloud}
  \item Advisor: \href{https://www.first.iir.titech.ac.jp/member/core3.html#miyamoto}{Associate Prof.~Tomoyuki Miyamoto}
\end{itemize}

\subsection{Changshu Institute of Technology}[Suzhou, China]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item Bachelor of Engineering in Optoelectronic Information Science and Technology  \\ \printdate{Sep 2017~--~Jun 2021}
  \item Thesis: {Mode Characteristics Analysis of The Ridged Waveguide}
  \item Advisor: Prof. Ming Yang
\end{itemize}

\section{Skills}

\begin{description}
  \item[Programming\&Hardware] Python, Matlab, STM32, C, Arduino, \LaTeX
  \item[Tools] Matlab, COMSOL, Lighttools
  \item[Languages\&Test] English(IELTS 7.0), Chinese(Native), Japanese(Primary), GRE 317
\end{description}

\section{Research \\ Interests}

\begin{itemize}
  \item Short-Mid-Long Range Optical Wireless Power Transmission
  \item Laser Safety and Automatic Laser Emission Control
  \item Vertical Cavity Surface Emitting Laser
  \item Object recognition and intrusion detection
\end{itemize}

\section{Selected \\ Publications}
\begin{enumerate}
	\item  Chen Zuo, and Tomoyuki Miyamoto. 2024. "Camera-Based Safety System for Optical Wireless Power Transmission Using Dynamic Safety-Distance" Photonics 11, no. 6: 500.
	\item  Chen Zuo, and Miyamoto Tomoyuki. 2023. “Improvement of Optical Wireless Power Transmission Safety System Using Depth Camera by New Safety Distance.” In The 5th Optical Wireless and Fiber Power Transmission Conference, OWPT11:05.
	\item Chen Zuo, and Miyamoto Tomoyuki. 2024. “Integrative Dynamic Safety System for OWPT: Real-Time Velocity and Distance-Based Safety Control.” In The 6th Optical Wireless and Fiber Power Transmission Conference, OWPT06:02. SPIE.
\end{enumerate}

%\publications[keyword={selected}]{publications.bib}

%{
%\footnotesize%
%\textsuperscript{\textdagger}These authors contributed equally.
%}

\section{Awards}

\begin{itemize}
  \item \href{https://educ.titech.ac.jp/ee/eng/news/2024_04/065884.html}{Outstanding Master Student Award} \printdate{2023}
  \item \href{https://www.first.iir.titech.ac.jp/news/2023/detail_1455.html}{Student Paper Award, OWPT2023} \printdate{2023}
  \item Excellent Undergraduate Thesis \printdate{2021}
  \item University Scholarship, Second \printdate{2021}
  \item University Scholarship, Second \printdate{2020}
  \item Unviersity Scholarship, First \printdate{2019}
  \item Excellent AIESEC Global Volunteer \printdate{2018}
\end{itemize}

\end{document}
